% !TEX TS-program = xelatex
\documentclass[11pt,a4paper]{article}

% ---------- PACKAGES ----------
\usepackage[a4paper,margin=1.5cm]{geometry}
\usepackage{parskip}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{bookmark}
\usepackage{setspace}
\usepackage{xcolor}
\usepackage{fontspec}
\usepackage{ragged2e}
\newcommand{\dotnet}{\mbox{.NET}}
% ---------- FONTS ----------
% Use a system sans font with full bold/italic shapes
\setmainfont{Manrope}[
    Path=./Manrope/,
    Scale=0.85,
    Extension = .ttf,
    UprightFont=*-Regular,
    BoldFont=*-Bold,
    % ItalicFont=*-Italic,
    % BoldItalicFont=*-BoldItalic
    ]
\setsansfont{Manrope}[
    Path=./Manrope/,
    Scale=0.85,
    Extension = .ttf,
    UprightFont=*-Regular,
    BoldFont=*-Bold,
    % ItalicFont=*-Italic,
    % BoldItalicFont=*-BoldItalic
    ]
\renewcommand{\familydefault}{\sfdefault}

% ---------- COLORS ----------
\definecolor{primary}{HTML}{0A66C2}
\definecolor{textgray}{HTML}{333333}
\definecolor{lightgray}{HTML}{666666}

% ---------- SECTION FORMATTING ----------
\titleformat{\section}{\large\bfseries\color{primary}}{}{0em}{}[\vspace{0.1\baselineskip}{\color{primary}\titlerule}]

% ---------- DOCUMENT ----------
\begin{document}
\frenchspacing
\hypersetup{hidelinks,breaklinks=true,pdfauthor={Jaival Saija},pdftitle={Cover Letter},pdfcreator={XeLaTeX}}
\setlength{\emergencystretch}{6em}
\sloppy

% ======= HEADER =======
\begin{center}
\begin{minipage}{0.92\textwidth}
\centering
    {\Huge\bfseries Jaival Saija}\\[0.5pt]
    {\large DevOps Engineer}\\[2pt]
    {\small
    \href{mailto:saijajaival@gmail.com}{saijajaival@gmail.com} \quad | \quad
    \href{https://jaivalsaija.vercel.app}{jaivalsaija.vercel.app} \quad | \quad
    \href{https://linkedin.com/in/jaivalsaija}{LinkedIn} \quad | \quad
    \href{https://github.com/Jaival}{GitHub} \quad | \quad
    \textcolor{lightgray}{Location: Kaiserslautern, Germany} \quad | \quad
    \textcolor{lightgray}{Contact Number: +49 1745126677}
    }
\end{minipage}
\end{center}

\vspace{4pt}

% ======= COVER LETTER =======
\section*{Cover Letter}

\textbf{Dear Hiring Manager,}

I am excited to apply for the DevOps Engineer position at your company. With hands-on experience supporting AWS-based production systems for a {\dotnet} CMS product and current graduate studies in Computer Science at RPTU, I bring a pragmatic approach to reliability, automation, and collaborative delivery.

\textbf{What I can bring to your team:}
\begin{itemize}[leftmargin=*, topsep=0pt, itemsep=0pt, parsep=0pt, partopsep=0pt]
    \item \textbf{Production-minded AWS support:} Monitored servers, performed upgrades/patching, and partnered with developers to resolve incidents and ship releases across multiple environments.
    \item \textbf{Faster, safer releases:} Streamlined deployment steps and authored runbooks/SOPs that reduced manual effort by 20\% and cut onboarding time by 30\%.
    \item \textbf{Clear communication:} Translated operational issues into clear action items, improving ticket turnaround times and cross-team alignment.
\end{itemize}

I took time away from full-time work to pursue my M.Sc., deepening my foundation in operating systems, networks, cloud computing, and machine learning. This period sharpened my ability to reason about performance, security, and scalability—skills I am eager to apply to real-world systems at your company.

I'm motivated by environments where uptime, feedback loops, and continuous improvement matter. I would welcome the opportunity to discuss how my background in AWS support, release coordination, and systematic problem-solving can help your company enhance reliability and ship faster with confidence.

Thank you for your time and consideration. I look forward to speaking with you.

\textbf{Sincerely,} \\
Jaival Saija

\end{document}


